% ============================================
% SPARROW AI - ElevenLabs Partnership Interest Letter
% ============================================

\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

% Colors
\definecolor{sparrowblue}{RGB}{37, 99, 235}
\definecolor{elevenlabspurple}{RGB}{138, 43, 226}

\hypersetup{
    colorlinks=true,
    linkcolor=sparrowblue,
    urlcolor=sparrowblue
}

\signature{Brian Mwai\\Founder, Sparrow AI\\Nairobi, Kenya}
\address{Sparrow AI\\Nairobi, Kenya\\sprrw.app}
\date{December 29, 2024}

\begin{document}

\begin{letter}{ElevenLabs Startup Program\\ElevenLabs, Inc.}

\opening{Dear ElevenLabs Team,}

I am writing to express my strong interest in joining the \textbf{ElevenLabs Startup Program} with Sparrow AI, an AI-powered sales training platform built on ElevenLabs Conversational AI.

\textbf{\large About Sparrow AI}

Sparrow AI enables sales professionals to practice cold calls, discovery conversations, and objection handling with realistic AI prospects that respond with natural voice. Our platform addresses a critical market need: 91\% of sales teams missed quota in 2024, largely due to inadequate practice opportunities.

\textbf{\large ElevenLabs Integration}

ElevenLabs is the core of our voice experience:

\begin{itemize}
\item \textbf{Conversational AI}: Powers all prospect interactions with natural, real-time voice
\item \textbf{Dynamic Variables}: Enables unique personas for every practice session
\item \textbf{Voice Library}: Multiple voices for different prospect personalities
\item \textbf{React SDK}: Seamless frontend integration
\end{itemize}

We have built our entire product around ElevenLabs' capabilities, demonstrating the power of voice AI in professional training applications.

\textbf{\large Market Opportunity}

\begin{itemize}
\item \textbf{TAM}: \$5.7B (B2B sales training in US)
\item \textbf{SAM}: \$1.5B (Inside sales reps)
\item \textbf{Target}: \$45M ARR by Year 5
\end{itemize}

The sales training market is ripe for voice AI disruption. Traditional training methods fail because sales is a performance skill that requires practice, not passive learning.

\textbf{\large Why ElevenLabs Partnership}

Joining the startup program would enable us to:

\begin{enumerate}
\item Scale our platform with additional API credits
\item Access advanced features for enhanced prospect realism
\item Collaborate on voice AI innovations in the sales training space
\item Serve as a showcase for ElevenLabs' Conversational AI capabilities
\end{enumerate}

\textbf{\large Traction}

\begin{itemize}
\item Fully functional MVP deployed at \url{https://sprrw.app}
\item Complete voice integration with persona generation
\item Real-time scoring and detailed feedback system
\item Open source repository with MIT license
\end{itemize}

\textbf{\large Commitment}

We are committed to building Sparrow AI as a long-term business, not just a hackathon project. ElevenLabs' voice AI technology is fundamental to our vision of transforming how sales professionals develop their skills.

I would welcome the opportunity to discuss how Sparrow AI can contribute to the ElevenLabs ecosystem while growing as a startup partner.

\closing{Sincerely,}

\vspace{1cm}

\textbf{Contact Information}\\
Email: hello@sprrw.app\\
GitHub: \url{https://github.com/brn-mwai}\\
Project: \url{https://sprrw.app}

\end{letter}

\end{document}
